Loblaws Seasonal Discount Patterns: Peak Sales Frequency in Fall and Deeper Discounts in Early Spring

### 2024-11-15 paper/paper.qmd
committing llm usage addition

Each entry in the data includes key attributes such as product_id, product_name, vendor, nowtime (the timestamp of the price check), and the prices themselves. This transformation process, from initial price observation to dataset entry, involves aggregating data from retailer websites, ensuring each record accurately reflects the status at the time of data collection. Thus, Project Hammer encapsulates the fluctuations and trends in product prices as a dataset, offering insights into seasonal pricing behavior, promotional impacts, and potential economic influences on retail prices. This structured dataset serves as a foundation for further analysis, translating the observed behavior of prices in the marketplace into quantifiable data for research.

>>>>

Each entry in the data includes key attributes such as product_id, product_name, vendor, nowtime (the timestamp of the price check), and the prices themselves. This transformation process, from initial price observation to dataset entry, involves aggregating data from retailer websites, ensuring each record accurately reflects the status at the time of data collection. Thus, Project Hammer captures the fluctuations and trends in product prices as a dataset, offering insights into seasonal pricing behavior, promotional impacts, and potential economic influences on retail prices. This structured dataset serves as a foundation for further analysis, translating the observed behavior of prices in the marketplace into quantifiable data for research.
